Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
remove mention to time-frequency scattering
time-scattering -> scattering

Irrespective of the rank $k$ considered, best result is achieved for the time-scattering with logarithmic compression using the \emph{ob-c} approach. Overall, the time scattering with the logarithmic compression outperform the MFCCs systematically.

@@

For both MFCCs and time-scattering, \emph{ob-c} and \emph{ob-w} outperform \emph{ei}, thus confirming the benefits of using an object-based representation to refine the similarity measures between the scenes. However, it is worth noticing that \emph{ob-a} perform equivalently to \emph{ei}, which shows that the discriminant information is not carried by all the centroids. To take advantage of an object-based representation, a selection step has to be run on the representatives of the scenes.

Lastly, we see that while \emph{ob-c} and \emph{ob-w} perform equivalently for the MFCCs, \emph{ob-c} seems to be able to better characterized the classes than \emph{ob-w} for the time scattering. This last observation suggests that weighted a centroid according to the number of frames belonging to it may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments  \gl{find examples} may shared a lot of similar sound sources \gl{reformulate}.

@@

In this paper, the benefit of considering 1) the scattering transform for building discriminant features and 2) unsupervised clustering for the modeling of large time span environmental acoustic scenes. Experiments shows that the time/frequency scattering achieves better discriminability than the time scattering one or MFCCs as they probably better isolate elements of interest in different information channels, thus allowing an efficient and scalable early integration process. This leads to improvement both for the ASSR and ASC tasks.

>>>>

\subsection{MFCC \vs scattering transform}

Irrespective of the rank $k$ considered, best result is achieved for the scattering transform with logarithmic compression using the \emph{ob-c} approach. Overall, log-compressed scattering coefficients systematically outperform MFCCs.

@@

For both MFCCs and scattering, \emph{ob-c} and \emph{ob-w} outperform \emph{ei}, thus confirming the benefits of using an object-based representation to refine the similarity measures between the scenes. However, it is worth noticing that \emph{ob-a} perform equivalently to \emph{ei}, which shows that the discriminant information is not carried by all the centroids. To take advantage of an object-based representation, a selection step has to be run on the representatives of the scenes.

Lastly, we see that while \emph{ob-c} and \emph{ob-w} perform equivalently for the MFCCs, \emph{ob-c} seems to be able to better characterize the classes than \emph{ob-w} for scattering coefficients. This last observation suggests that weighted a centroid according to the number of frames belonging to it may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments  \gl{find examples} may shared a lot of similar sound sources \gl{reformulate}.

@@

In this paper, the benefit of considering 1) the scattering transform for building discriminant features and 2) unsupervised clustering for the modeling of large time span environmental acoustic scenes.
This leads to improvement both for the ASSR and ASC tasks.
